Adaptive Shrinkage and False Discovery Rates by Laplace Approximation

### 2013-05-15 talks/ilike-slides.Rmd
final slides

* Prelude
* Allegro (ma non troppo)

@@

@@

>>>>

* Prelude
* Allegro (ma non troppo)
* Coda

@@

# Other Applications

- Widely applicable: perhaps anywhere (?) 
where shrinkage is appropriate, requiring only an estimated
effect size and standard error for each object.

- Could also use effect size estimate and $p$ value for each variable, by converting to effect size estimate and (pseudo-) standard error.

- Currently applying it to wavelet shrinkage applications.

# Guarantees?

- ``I think you have some nice ideas. How will you convince
people to use them?" (C Morris)

@@

# Coda: Other i-like related work

- Bayesian variable selection for large-scale linear regression.

- BSLMM: $$Y = X \beta + \epsilon,$$ with $\beta_j \sim 
\pi N(0,\sigma_b^2) + (1-\pi) N(0,\sigma_a^2+\sigma_b^2)$.

- Particular focus on prior specification (reparameterize in 
terms of regression $R^2$).

- BSLMM software, runs with thousands of individuals, hundreds
of thousands of variables. (Zhou et al, PloS Genetics 2013)

- Also variational approximations (Carbonetto and Stephens, Bayesian Analysis, 2012)
